Stellar and Planetary Properties of \KT\ Campaign 1 Candidates and Validation of \Nvalnew\ Systems, Including a Planet Receiving Earth-like Insolation

### 2015-06-22 ms.tex
tdm edits

In this work, we use
\texttt{vespa}\footnote{\url{http://github.com/timothydmorton/vespa}},
a new publicly available, general-purpose implementation
of the \citet{Morton12} procedure,
to calculate false positive probabilities (FPPs) for each of these
\KT\ candidates.
The following constraints on false positive
scenarios are imposed:
\begin{itemize}
\item A chance-aligned eclipsing binary system may reside anywhere inside
or within one pixel of the photometric aperture of the target star.
\change{In creating a light curve for each star, we define photometric apertures ranging
from 10 to 20 arcseconds for each star, as defined in Table 4.
Given the 6-arcsecond PSF of the \kep\ telescope, we allow for the possibility
that companions falling just outside of our aperture (within one pixel) may
contribute to the light curve, possibly causing a false positive event.
The search for such companions is discussed in
\textsection \ref{sec:background}.}
\item The maximum allowed depth of a potential secondary eclipse event
is the most significantly detected signal at the same
period of the planet candidate, once the primary transit is masked out
(discussed in \textsection\ref{sec:sec}).
\change{\texttt{vespa} does not allow for the possibility of secondary eclipses
larger than those observed in the \KT\ light curve for each star.}
\item Blended stars must be allowed by the available adaptive optics
and archival imaging data (discussed in detail in \textsection
\ref{sec:AO} and \ref{sec:background}).
\change{\texttt{vespa} only considers stars below the detection threshold for
the AO imaging, which is a position-dependent value following a calculated
contrast curve for each star.}
\end{itemize}

>>>>

In this work, we use
\texttt{vespa}\footnote{\url{http://github.com/timothydmorton/vespa}} \citep{vespa},
a new publicly available, general-purpose implementation
of the \citet{Morton12} procedure,
to calculate false positive probabilities (FPPs) for each of these
\KT\ candidates.
The following constraints on false positive
scenarios are imposed:
\begin{itemize}
\item A chance-aligned eclipsing binary system may reside anywhere inside
or within one pixel of the photometric aperture of the target star.
\change{In creating a light curve for each star, we define photometric apertures ranging
from 10 to 20 arcseconds for each star, as defined in Table 4.
Given the 6-arcsecond PSF of the \kep\ telescope, we allow for the possibility
that companions falling just outside of our aperture (within one pixel) may
contribute to the light curve, possibly causing a false positive event.
The search for such companions is discussed in
\textsection \ref{sec:background}.}
\item The maximum allowed depth of a potential secondary eclipse event
is the most significantly detected signal at the same
period of the planet candidate, once the primary transit is masked out
(discussed in \textsection\ref{sec:sec}).
\change{\texttt{vespa} does not allow for the possibility of secondary eclipses
larger than those observed in the \KT\ light curve for each star.}
\item Blended stars must be allowed by the available adaptive optics
and archival imaging data (discussed in detail in \textsection
\ref{sec:AO} and \ref{sec:background}).
\change{\texttt{vespa} only considers stars below the detection threshold for
the AO imaging, which is a position-dependent value following a calculated
contrast curve for each star.}
\end{itemize}
